Causal Compatibility Inequalities Admitting Quantum Violations in the Triangle Structure

### 2020-08-07 CCIAQVTS/CCIAQVTS.tex
added links to the published errata in footnotes marking locations of the errors

    \subsection{The WagonWheel Inequality}
    The first causal compatibility inequality chosen for presentation is reported below:
    \begin{equation*}
    \begin{gathered}
        \eq\label[ineq]{eq:ww_ineq}
        I\tsb{WagonWheel} : \\
        -P_{A_{l}B_{l}}(10)
        +P_{A_{l}B_{l}C_{l}C_{r}}(1010)
        -P_{A_{l}B_{l}}(01) P_{C_{l}C_{r}}(10)
        -P_{C_{l}C_{r}}(00) P_{C_{l}C_{r}}(11) \\
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(100110)
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(110010) \\
        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(101111)
        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(111011) \\
        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(001001)
        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(011101) \\
        +P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(000000)
        +P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(010100) \\
        \leq 0
    \end{gathered}
    \end{equation*}

@@

    By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle structure per \cref{eq:triangle_compatibility} must satisfy $I\tsb{WagonWheel}$. On the other hand, the Fritz distribution violates $I\tsb{WagonWheel}$ with violation $\f{1}{16}(\sqrt{2} - 1) \not \leq 0$. Consequently we affirm that the Fritz distribution is incompatible with the Triangle structure, a fact previously only demonstrated without inequalities.

>>>>

    \subsection{The WagonWheel Inequality}
    The first causal compatibility inequality chosen for presentation is reported below:\footnote{\label{foot:error}In earlier versions of this paper, including the version published in Physical Review A (found here: \url{https://journals.aps.org/pra/abstract/10.1103/PhysRevA.98.022113}) and the initial arXiv submission, \Cref{eq:ww_ineq} was incorrectly presented. A detailed errata can be found here: \url{https://journals.aps.org/pra/abstract/10.1103/PhysRevA.102.029901}.}

    \begin{equation*}
    \begin{gathered}
        \eq\label[ineq]{eq:ww_ineq}
        I\tsb{WagonWheel} : \\
        -P_{A_{l}B_{l}}(10)
        +P_{A_{l}B_{l}C_{l}C_{r}}(1010)
        -P_{A_{l}B_{l}}(01) P_{C_{l}C_{r}}(10)
        -P_{C_{l}C_{r}}(00) P_{C_{l}C_{r}}(11) \\
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(100110)
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(110010) \\
        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(101111)
        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(111011) \\
        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(001001)
        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(011101) \\
        +P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(000000)
        +P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(010100) \\
        \leq 0
    \end{gathered}
    \end{equation*}

@@

    By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle structure per \cref{eq:triangle_compatibility} must satisfy $I\tsb{WagonWheel}$. On the other hand, the Fritz distribution violates $I\tsb{WagonWheel}$ with violation $\f{1}{16}(\sqrt{2} - 1) \not \leq 0$\footnote{As a result of the error mentioned in Footnote~\ref{foot:error}, earlier versions of this paper erroneously reported a numerical violation of $\f{1}{16} \not \leq 0$. }. Consequently we affirm that the Fritz distribution is incompatible with the Triangle structure, a fact previously only demonstrated without inequalities.
